Modelling BCG vaccination in the UK

### 2019-07-15 rmds/04-tb-epi-england.Rmd
updated labelling

In this chapter I explore the epidemiology of TB in England using routine data-sets, with a particular focus on the impact of missing data, the mechanisms underlying that missing date, seasonal trends, the role of age, UK birth status and BCG status. I have also estimated incidence rates, stratified by UK birth status and age, which I then used to identify trends in TB incidence over time. Finally I report TB outcomes in England using case rates, again stratified by BCG status and UK birth status. These data will then be used throughout this thesis to explore the impact of BCG vaccination on TB outcomes (Chapter \@ref(benefical-bcg-out)), to estimate the direct impact of the 2005 change in BCG vaccination policy (Chapter \@ref(direct-eff)), to parameterise a dynamic TB transmission model (Chapter \@ref(model-development)) and to fit the same model to data (Chapter \@ref(model-fitting)).

@@

Findings from this chapter are used throughout the later chapters of this thesis. In particular, Chapter  \@ref(benefical-bcg-out) uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter \@ref(direct-eff) explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter \@ref(model-development) uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter \@ref(model-fitting) uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model.

@@

- Findings from this chapter are used throughout the later chapters of this thesis; to inform analysis questions (Chapter  \@ref(benefical-bcg-out) and \@ref(direct-eff)), identify variables for which missing data must be imputed (Chapter  \@ref(benefical-bcg-out) and \@ref(direct-eff)), to parameterise a dynamic TB transmission model (Chapter \@ref(model-development)), and to fit a dynamic TB transmission model (Chapter \@ref(model-fitting)).

>>>>

In this chapter I explore the epidemiology of TB in England using routine data-sets, with a particular focus on the impact of missing data, the mechanisms underlying that missing date, seasonal trends, the role of age, UK birth status and BCG status. I have also estimated incidence rates, stratified by UK birth status and age, which I then used to identify trends in TB incidence over time. Finally I report TB outcomes in England using case rates, again stratified by BCG status and UK birth status. These data will then be used throughout this thesis to explore the impact of BCG vaccination on TB outcomes (Chapter \@ref(beneficial-bcg-out)), to estimate the direct impact of the 2005 change in BCG vaccination policy (Chapter \@ref(direct-eff)), to parameterise a dynamic TB transmission model (Chapter \@ref(model-development)) and to fit the same model to data (Chapter \@ref(model-fitting)).

@@

Findings from this chapter are used throughout the later chapters of this thesis. In particular, Chapter  \@ref(beneficial-bcg-out) uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter \@ref(direct-eff) explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter \@ref(model-development) uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter \@ref(model-fitting) uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model.

@@

- Findings from this chapter are used throughout the later chapters of this thesis; to inform analysis questions (Chapter  \@ref(beneficial-bcg-out) and \@ref(direct-eff)), identify variables for which missing data must be imputed (Chapter  \@ref(beneficial-bcg-out) and \@ref(direct-eff)), to parameterise a dynamic TB transmission model (Chapter \@ref(model-development)), and to fit a dynamic TB transmission model (Chapter \@ref(model-fitting)).
